### 2017-01-23 doc/manuscript.Rmd
Second draft of intro

Note: keep the story simple and clean, without getting too dense

- Run PLS with just those FA that loaded strongly to see the predictive ability.
- SA with/without NEFA
- SA with/without WC
- Interactions of VN unadjusted

@@

- Primary analysis:
    - Look over medications, how they influence the TAGFA
    - GEE
        - SA for the large outlier for the TAGFA (see dist plot)
        - Include # of both uncorrected and corrected (FDR) significant associations
        - QIC modeling
        - DAG development
        - Look over the entire model (see which variables are significant, etc)
        - Sensitivity analysis with Carb intake? And with adiponectin? (which is
        involved in TAG metabolism)
    - PLS with ISI and HOMA-IR
        - Use extracted PLS components in GEE (?)
- Secondary analysis:
    - AROC
        - dysgly with clinical TAG vs the 'best' fatty acid to compare to

- Make sure to include comments from NEFA paper
- Add stats to basic char table... (don't really want to. But I should ..?)

Possible interpretations:

- muscle IR -> higher TAG
- But longitudinal, since no interaction with time, so maybe the higher TAG is
because of higher IR (since this population is at risk of being IR).

@@

Title: Fatty acids involved in de novo lipogenesis within triacylglycerol fraction strongly predict lower insulin sensitivity.

@@

Hypertriglyceridemia is an established and well known factor involved in the
dysregulation of metabolic function and subsequent negative health impacts. It
is a component of the metabolic syndrome {{ cite }}, a strong risk factor for
cardiovascular disease {{cite}}, and can contribute to worsening pathogenesis of
diabetes through it's harmful health effects {{ clarify }}. Triacylglcerol (TAG)
is a common blood measure taken during routine clinical visits and has {{
historically?}} been a target of pharmaceutical intervention {{cite}}, though evidence on
the {{efficacy? effectiveness?}} of such interventions are often underwhelming
on their effects on disease {{risk?}} reduction {{cite}}.

TAG as a pharmaceutical target and as a measure of metabolic health is a single
measure of all fatty acids within the TAG fraction. However, given the 
increasing appreciation for the role of the specific fatty acid composition
of various blood lipid fractions on health outcomes, reducing the complex fatty acids 
metabolism within the TAG fraction to a single measure may contribute to the 
less than expected {{?}} changes in risk reduction.

In additiona, the {{interplay?}} between TAG and IR is complex and has the
potential to act as a {{feed forward?}} loop. Greater resistance to insulin,
particularly in the liver, can result in greater accumulation of hepatic fat and
a potential associated increased production in TAG which are secreted into
circulation with VLDL [@Yu2012a] {{review on mechanisms of TAG, IR, etc.}} {{not
always the case, dependent on ethnicity}}. However, higher circulating TAG can
exacerbate or contribute to insulin resistance in various tissues, creating a
vicious cycle {{cite}}. Few studies have been conducted that have examined the
longitudinal effect of TAGFA composition on diabetes pathophysiology.

Several prospective studies have identified to date the association of 
hypertriglyceridemia on incident diabetes {{[@Chien2008a; @DAgostino2004a;
@Schulze2009a]}}, but no longitudinal studies have been conducted{{another 
word?}} on the pathophysiological factors underlying diabetes.

Our objective was to examine the longitudinal role of the specific composition
of the serum TAG fraction on OGTT-derived measures of insulin sensitivity and
beta-cell function in an Canadian population at risk for diabetes over 6 years.

>>>>

@@

- Primary analysis:
        - Sensitivity analysis with Carb intake?

@@

Title: Fatty acids involved in de novo lipogenesis within the serum
triacylglycerol fraction strongly predict lower insulin sensitivity.

@@

Hypertriglyceridemia is an extensively studied and well known factor involved in
the dysregulation of metabolic function and subsequent negative health impacts.
It is a component of the metabolic syndrome [@Alberti2009], a strong risk factor for
cardiovascular disease [@DAgostino2004a], and can contribute to the pathogenesis
of diabetes. Measuring triacylglcerides (TAG) within the blood is commonly done
during routine clinical visits as part of health assessment. However, clinically
measured TAG is limited as it represents all the types of fatty acids within the
TAG fraction as a single measure. Given the increasing appreciation for the role
of the specific fatty acid composition on health outcomes, for instance with
differences in associations of fatty acids within the PL lipid fraction
[@Forouhi2014a; @Ma2015a] including an analysis from the PROMISE cohort
[@Johnston2016a], there are relatively few studies that have explored this area
of research in the TAG fraction.

The interaction between TAG and insulin sensitivity is complex and has 
components of a feedback system. Greater resistance to insulin in both the liver
and muscle may result in greater production of TAG and secretion of lipoproteins
that transport TAG [@Yu2012a]. Likewise, greater TAGFA may contribute to 
metabolic dysfunction and lipotoxicity in various tissues, such as the 
beta-cells, and thus continuing the cycle. Given the complexity and temporal
nature of the relationship, long term studies with multiple data collections are
paramount to better understanding the underlying biology and subsequent risk.

While several prospective studies have identified a harmful association of 
hypertriglyceridemia on greater incidence for type 2 diabetes 
[@Chien2008a; @DAgostino2004a; @Schulze2009a], there are limited longitudinal
studies that have examined the relationship between TAG and it's composition on
the pathophysiological factors underlying diabetes, particularly in regard to
beta-cell function. Our objective was to examine the longitudinal role of the
specific composition of the serum TAG fraction on OGTT-derived measures of
insulin sensitivity and beta-cell function in an Canadian population at risk for
diabetes.
